Baseline Travel Survey Summary ITHIM-R

### 2021-11-24 code/producing_trips_rd/trip-summary.Rmd
Changing names of files and population in some cases

```{r,  comment=NA, message=FALSE, warning=FALSE, prompt=FALSE, cache=FALSE, echo=F}
trip <- read_csv("data/local/buenos_aires/buenos_aires_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Buenos_Aires <- value

trip <- read_csv("data/local/sao_paulo/sao_paulo_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Sao_Paulo <- value

trip <- read_csv("data/local/belo_horizonte/belo_horizonte_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Belo_Horizonte <- value

trip <- read_csv("data/local/mexico_city/mexico_city_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Mexico <- value

@@

trip <- read_csv("data/local/santiago/santiago_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Santiago <- value

trip <- read_csv("data/local/vizag/vizag_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Visakhapatnam <- value

trip <- read_csv("data/local/delhi/delhi_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Delhi <- value

trip <- read_csv("data/local/bangalore/bangalore_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Bangalore <- value

trip <- read_csv("data/local/accra/accra_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Accra <- value

trip <- read_csv("data/local/cape_town/cape_town_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Cape_Town <- value

@@

```{r,  comment=NA, message=FALSE, warning=FALSE, prompt=FALSE, cache=FALSE, echo=F}
trip <- read_csv("data/local/buenos_aires/buenos_aires_trip.csv",
                 guess_max = 100000)
quality_check(trip, 15, 69)
trip_summary2$Buenos_Aires <- value

trip <- read_csv("data/local/sao_paulo/sao_paulo_trip.csv",
                 guess_max = 100000)
quality_check(trip, 15, 69)
trip_summary2$Sao_Paulo <- value

trip <- read_csv("data/local/belo_horizonte/belo_horizonte_trip.csv",
                 guess_max = 100000)
quality_check(trip, 15, 69)
trip_summary2$Belo_Horizonte <- value

trip <- read_csv("data/local/mexico_city/mexico_city_trip.csv",
                 guess_max = 100000)
quality_check(trip, 15, 69)
trip_summary2$Mexico <- value

@@

trip <- read_csv("data/local/santiago/santiago_trip.csv",
                 guess_max = 100000)
quality_check(trip, 15, 69)
trip_summary2$Santiago <- value

trip <- read_csv("data/local/vizag/vizag_trip.csv",
                 guess_max = 100000)
quality_check(trip, 15, 69)
trip_summary2$Visakhapatnam <- value

trip <- read_csv("data/local/delhi/delhi_trip.csv",
                 guess_max = 100000)
quality_check(trip, 15, 69)
trip_summary2$Delhi <- value

trip <- read_csv("data/local/bangalore/bangalore_trip.csv",
                 guess_max = 100000)
quality_check(trip, 15, 69)
trip_summary2$Bangalore <- value

trip <- read_csv("data/local/accra/accra_trip.csv",
                 guess_max = 100000)
quality_check(trip, 15, 69)
trip_summary2$Accra <- value

trip <- read_csv("data/local/cape_town/cape_town_trip.csv",
                 guess_max = 100000)
quality_check(trip, 15, 69)
trip_summary2$Cape_Town <- value

>>>>

```{r,  comment=NA, message=FALSE, warning=FALSE, prompt=FALSE, cache=FALSE, echo=F}
trip <- read_csv("data/local/buenos_aires/buenos_aires_trips.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Buenos_Aires <- value

trip <- read_csv("data/local/sao_paulo/sao_paulo_trips.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Sao_Paulo <- value

trip <- read_csv("data/local/belo_horizonte/belo_horizonte_trips.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Belo_Horizonte <- value

trip <- read_csv("data/local/mexico_city/mexico_city_trips.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Mexico <- value

@@

trip <- read_csv("data/local/santiago/santiago_trips.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Santiago <- value

trip <- read_csv("data/local/vizag/vizag_trips.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Visakhapatnam <- value

trip <- read_csv("data/local/delhi/delhi_trips.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Delhi <- value

trip <- read_csv("data/local/bangalore/bangalore_trips.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Bangalore <- value

trip <- read_csv("data/local/accra/accra_trips.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Accra <- value

trip <- read_csv("data/local/cape_town/cape_town_trips.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Cape_Town <- value

@@

```{r,  comment=NA, message=FALSE, warning=FALSE, prompt=FALSE, cache=FALSE, echo=F}
trip <- read_csv("data/local/buenos_aires/buenos_aires_trips.csv",
                 guess_max = 100000)
quality_check(trip, 15, 69)
trip_summary2$Buenos_Aires <- value

trip <- read_csv("data/local/sao_paulo/sao_paulo_trips.csv",
                 guess_max = 100000)
quality_check(trip, 15, 69)
trip_summary2$Sao_Paulo <- value

trip <- read_csv("data/local/belo_horizonte/belo_horizonte_trips.csv",
                 guess_max = 100000)
quality_check(trip, 15, 69)
trip_summary2$Belo_Horizonte <- value

trip <- read_csv("data/local/mexico_city/mexico_city_trips.csv",
                 guess_max = 100000)
quality_check(trip, 15, 69)
trip_summary2$Mexico <- value

@@

trip <- read_csv("data/local/santiago/santiago_trips.csv",
                 guess_max = 100000)
quality_check(trip, 15, 69)
trip_summary2$Santiago <- value

trip <- read_csv("data/local/vizag/vizag_trips.csv",
                 guess_max = 100000)
quality_check(trip, 15, 69)
trip_summary2$Visakhapatnam <- value

trip <- read_csv("data/local/delhi/delhi_trips.csv",
                 guess_max = 100000)
quality_check(trip, 15, 69)
trip_summary2$Delhi <- value

trip <- read_csv("data/local/bangalore/bangalore_trips.csv",
                 guess_max = 100000)
quality_check(trip, 15, 69)
trip_summary2$Bangalore <- value

trip <- read_csv("data/local/accra/accra_trips.csv",
                 guess_max = 100000)
quality_check(trip, 15, 69)
trip_summary2$Accra <- value

trip <- read_csv("data/local/cape_town/cape_town_trips.csv",
                 guess_max = 100000)
quality_check(trip, 15, 69)
trip_summary2$Cape_Town <- value
